### 2015-02-22 fundamentals/fcsreqs.tex
Overhaul motivation and fcsreqs

@@

\subsubsection{Open Access}

\subsubsection{Flexibility and Extensibility}

In addition to being inaccessible, the vast majority of fuel cycle simulators
are, effectively, inextensible. Typical fuel cycle simulator development teams are insular, in
part due to aforementioned accessibility issues. Accordingly, their frameworks
typically contain heuristics and assumptions that constrain developer additions.

For example, most current simulators describe a finite set of acceptable
cycle constructions (once through, single-pass, multi-pass). That limits the
capability to create novel material flows and economic scenarios. The \Cyclus
simulation logic relies on a market paradigm, parameterized by the user, which
flexibly simulates dynamic responses to pricing, availability, and other
institutional preferences. This is an advanced level of flexibility that does
not exist in other fuel cycle simulators.

>>>>

\subsubsection{Open Access and Development Practices}

Moreover, both technical and institutional aspects of the software development
practices employed by the \Cyclus community faciltate collaboration.
Technically, \Cyclus employs a set of tools commonly used collaborative
software development that reduce the effort required to comment on, test and
ultimately merge individual contributions into the main development path.  
For many of the simulation platforms adopted by previous simulators, there were
technical obstacles that impeded this kind of collaboration.
Institutionally, \Cyclus invites all participants to propose, discuss and
provide input to the final decision making for all important changes.

\subsubsection{Modularity and Extensibility}

Modularity is a key enabler of extending the scope of fuel cycle analysis
within the \Cyclus framework.  Changes that are required to improve the
fidelity of modeling a paticular agent, or to introduce entirely new agents,
are narrowly confined and place no new requirements on the \Cyclus kernel.
Furthermore, there are very few assumptions or heuristics that would otherwise
restrict the algorithmic complexity that can be used to model the behavior of
such agents.

For example, most current simulators describe a finite set of acceptable cycle
constructions (once through, single-pass, multi-pass). That limits the
capability to create novel material flows and economic scenarios. The \Cyclus
simulation logic relies on a market paradigm, parameterized by the user, which
flexibly simulates dynamic responses to pricing, availability, and other
institutional preferences.

This minimal set of mutual dependencies between the kernel and the agents is
expressed through the \gls{DRE} that provides a level of flexibility that does
not exist in other fuel cycle simulators.  It creates the potential for novel
agent archetypes to interact with existing archetypes as they enter and leave
the simulation over time and seek to trade materials whose specific
composition may not be known \textit{a priori}.

@@

### 2015-02-22 fundamentals/intro.tex
Overhaul motivation and fcsreqs

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community. This essential capability is absent in
previous simulators where user customization and extensibility were not design
objectives, and was attained by the \emph{modular and open architecture} of
\Cyclus.  Additionally, \Cyclus facilitates direct comparison of modeling
methodologies with \emph{agent interchangeability}.  Finally, \Cyclus is
applicable to a broader range of fidelities, scales, and applications than
other simulators, due to the flexibility and generality of its
\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.

>>>>

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community to achieve two important goals: lower the
barrier for innvoative nuclear technologies to be included in fuel cycle analysis 
while improving the ability to compare simulations with and without those innovative
concepts.  This essential capability is absent in
previous simulators where user customization and extensibility were not design
objectives.  While the \emph{modular and open architecture} of
\Cyclus is necessary to meet these goals, it is not sufficient.  
\emph{Agent interchangeability} is required to facilitates direct comparison 
of alternative modeling methodologies and facility concepts.  Finally, \Cyclus is
applicable to a broader range of fidelities, scales, and applications than
other simulators, due to the flexibility and generality of its
\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.
